A Formal Model of Checked C

### 2023-01-16 sandp23/implementation.tex
add ACM
update.

\subsubsection{Generating~\cregion Source Partition}
\label{subsub:gencregion}
We copy all non-tainted functions into~\cregion source files and make the following modifications to enable interaction with~\ucregion (\ie sandboxed code).

We created a library once and for all for each sandbox.
This library abstracts the sandbox-specific details and exposes a uniform interface (header file) to be used in~\cregion.
For instance,~\code{_SBX_()} gets an opaque pointer to the target sandbox.

@@

\subsection{Supporting General Partioning Use Case}
\input{figures/newusecase}

@@

However, as mentioned in~\sect{subsec:checkedc}, checked pointers can be used alongside regular pointers, so the~\cregion{}~\emph{can} contain regular (unchecked) pointers as well.
%
This allows for flexibility in how the program is partitioned, such as only tainting a few high-risk unchecked functions rather than all of them. In this way, the system can be used as a generic program partitioning technique that balances the trade-off between overhead and security assurance.

For our example in~\lst{lst:final}, we can make only the function \code{process_req1} as tainted, thereby transitioning into a sandbox only when the corresponding (high-risk) request is received.

The general guidelines for this alternative use case are shown in~\fig{fig:mixedmodesupport}.
It is best to annotate all functions with checked types for security purposes. However, if it is difficult to convert all functions, it may be more practical to only mark certain high-risk functions with a high probability of vulnerabilities as tainted. This allows for a flexible partitioning system that balances the need for security assurance with the overhead of converting to~\checkedc.
We add the additional constraint of not allowing casting from taint types to generic types to enable this generic use case without violating the safety guarantees of~\systemname.
Specifically, we disallow the following casting in~\cregion:
\begin{minted}[mathescape, escapeinside=||, fontsize=\tiny]{diff}
//_t_Ptr<int> y; int *z;
|\faRemove| z = (int *)y; // Not allowed.
\end{minted}
\iffalse

>>>>

\subsubsection{Generating~\cregion Source Partition}
\label{subsub:gencregion}
We copy all non-tainted functions into~\cregion source files and make the following modifications to enable interaction with~\ucregion (\ie sandboxed code).
We created a library once and for all for each sandbox.
This library abstracts the sandbox-specific details and exposes a uniform interface (header file) to be used in~\cregion.
For instance,~\code{_SBX_()} gets an opaque pointer to the target sandbox.

@@

\subsection{Having Non-sandboxed Pointers}
\input{figures/newusecase}

@@

However, as mentioned in~\sect{subsec:checkedc}, checked pointers can be used alongside regular pointers, so the~\cregion{}~\emph{can} contain regular (unchecked) pointers as well.
This allows for flexibility in how the program is partitioned, such as only tainting a few high-risk unchecked functions rather than all of them. 
For our example in~\lst{lst:final}, we can make only the function \code{process_req1} as tainted, thereby transitioning into a sandbox only when the corresponding (high-risk) request is received.

In this way, the system can be used as a generic program partitioning technique that balances the trade-off between overhead and security assurance.
The general guidelines for this alternative use case are shown in~\fig{fig:mixedmodesupport}.
It is best to annotate all functions with checked types for security purposes. However, if it is difficult to convert all functions, it may be more practical to only mark certain high-risk functions with a high probability of vulnerabilities as tainted,
which maintains the assurance and overhead balance.
We add the additional constraint of not allowing casting from taint types to generic types to enable this generic use case without violating the safety guarantees of~\systemname.
Specifically, we disallow the following casting in~\cregion:
\begin{minted}[mathescape, escapeinside=||, fontsize=\tiny]{diff}
//_t_Ptr<int> y; int *z;
|\faRemove| z = (int *)y; // Not allowed.
\end{minted}
\iffalse
